Covariate adjustments on GTEx data (Skeletal Muscle)

### 2016-09-26 code/Rmd/GTEx_SkeletalMuscle.Rmd
Minor modifications

@@

p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color = as.factor(SMCENTER), size = SMRIN))
p <- p + theme_bw() + theme(legend.position="top") 
# p <- p + geom_text(aes(label= ID), size=4, hjust=0)
p

>>>>

library(synapseClient)
library(knitr)
library(githubr)

@@

p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color = SMNABTCH, shape = GENDER, size = SMRIN))
p <- p + theme_bw() + theme(legend.position="top") 
# p <- p + geom_text(aes(label= ID), size=4, hjust=0)
p
